---
title: "GOT_opgave"
author: "KGKK"
date: "2022-12-02"
output: html_document
---

#Loauding Packages
```{r}
library(tidyverse)
library(here)
library(pdftools)
library(tidytext)
library(textdata) 
library(ggwordcloud)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Locating A Game of Thrones text
```{r}
got_path <- here("data","got.pdf")
got_text <- pdf_text(got_path)
```

#Extracting the data from A Game of Thrones
```{r}
got_df <- data.frame(got_text) %>% 
  mutate(text_full = str_split(got_text, pattern = '\\n')) %>% 
  unnest(text_full) %>% 
  mutate(text_full = str_trim(text_full)) 
```

#Seperating into lines
```{r}
got_tokens <- got_df %>% 
  unnest_tokens(word, text_full)
```

#Counting all of the words
```{r count-words}
got_wc <- got_tokens %>% 
  count(word) %>% 
  arrange(-n)
got_wc
```
#Removing the stop words from data
```{r stopwords}
got_stop <- got_tokens %>% 
  anti_join(stop_words) %>% 
  select(-got_text)
```
#Chexking the wordcount again
```{r count-words2}
got_swc <- got_stop %>% 
  count(word) %>% 
  arrange(-n)
```
#Removing numbers
```{r}
got_no_numeric <- got_stop %>% 
  filter(is.na(as.numeric(word)))
```
#Selecting the top 100 words for the wordcloud
```{r}
got_top100 <- got_no_numeric %>% 
  count(word) %>% 
  arrange(-n) %>% 
  head(100)
```
#Creating a wordcloud
```{r wordcloud}
got_cloud <- ggplot(data = got_top100, aes(label = word)) +
  geom_text_wordcloud() +
  theme_minimal()
```
#Customizing the wordcloud
```{r wordcloud}
ggplot(data = got_top100, aes(label = word, size = n)) +
  geom_text_wordcloud_area(aes(color = n), shape = "diamond") +
  scale_size_area(max_size = 12) +
  scale_color_gradientn(colors = c("darkgreen","blue","red")) +
  theme_minimal()
```
#Implementing the "afinn", "bing" and "nrc" sentiment word rank
```{r}
get_sentiments(lexicon = "afinn")
get_sentiments(lexicon = "bing")
get_sentiments(lexicon = "nrc")
```
#Binding the words in "got_stop" to "afinn" word list
```{r bind-afinn}
got_afinn <- got_stop %>% 
  inner_join(get_sentiments("afinn"))
```

#Ranking
```{r count-afinn}
got_afinn_hist <- got_afinn %>% 
  count(value)
```

#Plotting
```{r count-afinn}
ggplot(data = got_afinn_hist, aes(x = value, y = n)) +
  geom_col()
```


