---
title: "Twist_exam"
author: "KGKK"
date: "2022-12-12"
output: html_document
---

```{r Loading Packages}
library(tidyverse)
library(here)
library(pdftools)
library(tidytext)
library(textdata) 
library(ggwordcloud)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r Using gutenbergr to download file}
install.packages("gutenbergr")
install.packages("devtools")
devtools::install_github("ropensci/gutenbergr")
library(dplyr)
library(gutenbergr)
gutenberg_download(730)
```
```{r naming the file}
twist <- gutenberg_download(730)
```


```{r seperating into words}
twist%>% 
  unnest_tokens(word, text) -> twist_tidy

```

```{r sorting by most used words}
twist_tidy %>% 
  count(word, sort = TRUE)
```

twist_text <- data.table::fwrite((twist_tidy))

count(x, ..., wt = NULL, sort = FALSE, name = NULL)
tally(x, wt = NULL, sort = FALSE, name = NULL)
add_count(x, ..., wt = NULL, sort = FALSE, name = NULL, .drop = deprecated())
add_tally(x, wt = NULL, sort = FALSE, name = NULL)


```{r removing stopwords}
twist_stop <- twist_tidy %>% 
  anti_join(stop_words)
```
#Checking the wordcount again
```{r count-words2}
twist_swc <- twist_stop %>% 
  count(word) %>% 
  arrange(-n)
```

#Removing numbers
```{r}
twist_no_numeric <- twist_stop %>% 
  filter(is.na(as.numeric(word)))
```

#Selecting the top 100 words for the wordcloud
```{r}
twist_top100 <- twist_no_numeric %>% 
  count(word) %>% 
  arrange(-n) %>% 
  head(100)
```

#Creating a wordcloud
```{r wordcloud}
twist_cloud <- ggplot(data = twist_top100, aes(label = word)) +
  geom_text_wordcloud() +
  theme_minimal()
```

#Customizing the wordcloud
```{r wordcloud}
ggplot(data = twist_top100, aes(label = word, size = n)) +
  geom_text_wordcloud_area(aes(color = n), shape = "diamond") +
  scale_size_area(max_size = 12) +
  scale_color_gradientn(colors = c("darkgreen","blue","red")) +
  theme_minimal()
```

#Implementing the "afinn", "bing" and "nrc" sentiment word rank
```{r}
get_sentiments(lexicon = "afinn")
get_sentiments(lexicon = "bing")
get_sentiments(lexicon = "nrc")
```


```{r binding afinn}
twist_afinn <- twist_stop %>% 
  inner_join(get_sentiments("afinn"))
```

```{r Ranking with Afinn}
twist_afinn_hist <- twist_afinn %>% 
  count(value)
```

```{r Plotting}
ggplot(data = twist_afinn_hist, aes(x = value, y = n)) +
  geom_col(fill = "olivedrab")
```

```{r}
twist_afinn %>% 
  filter(value == -5)
```

```{r}
twist_afinn %>% 
  filter(value == -4)
```

```{r}
twist_afinn %>% 
  filter(value == -3)
```